I've Got Nothing to Hide: \\ Exploring Privacy in Art, Fiction, and Film

### 2013-09-27 nothing_to_hide/presentation.tex
First draft.

% items enclosed in square brackets are optional; explanation below
\title[Privacy in Art, Books, and Film]{I've Got Nothing to Hide: \\
  Exploring Privacy in Art, Books, and Film}
\author[Josh Datko]{Joshua Datko}
\institute[Drexel]{
  Department of Computer Science\\
  Drexel University\\
  Philadelphia, PA 19103\\[1ex]
  \texttt{jbd65@drexel.edu}
}
\date[September 2013]{September 28, 2013}

@@

@@

    \begin{block}{}
      Privacy in Art.
    \end{block}

@@

@@

    \begin{block}{}
      Privacy in Fiction.
    \end{block}

@@

    \begin{block}{}
      Privacy in Film.
    \end{block}

@@

>>>>

% items enclosed in square brackets are optional; explanation below
\title[Privacy in Art, Fiction, and Film]{I've Got Nothing to Hide: \\
  Exploring Privacy in Art, Fiction, and Film}
\author[Josh Datko]{Joshua Datko}
\institute[Drexel]{
  Department of Computer Science\\
  Drexel University\\
  Philadelphia, PA 19103\\[1ex]
  \texttt{jbd65@drexel.edu}
}
\date[September 2013]{September 28, 2013}

@@

\AtBeginSection[]
{
  \begin{frame}{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}

}
\section{Article Summary}

@@

\begin{frame}
\frametitle{A Tale of Two Dystopias}
\begin{itemize}
\item Orwellian
  \begin{itemize}
  \item Surveillance state.
  \item Social control through over presence.
  \end{itemize}
\item Kafkaesque
  \begin{itemize}
  \item Information processing affects the power relationship.
  \item Frustrate individuals and creates helplessness and powerlessness.
  \end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{The problem with the argument}

The argument is built on the ``premise that privacy is about hiding a
wrong'' (Bruce Schneier).

\begin{itemize}
\item No Fourth Amendment protection to data stored by third parties.
\item Causes a chilling effect on Free Speech and Free Association.
\item Secondary Use: Unintended use of the collected data.

\begin{frame}
\frametitle{Final Point}

The issue, however, often is not whether the NSA or other government
agencies should be allowed to engage in particular forms of information
gathering; rather, it is what kinds of oversight and accountability we
want in place when the government engages in searches and seizures.

\section{Privacy in Art}

%% \begin{frame}

%% \begin{columns}[c] % the "c" option specifies center vertical alignment
%%     \column{.5\textwidth} % column designated by a command

%%     \begin{block}{}
%%       Privacy in Art.
%%     \end{block}

%%     \column{.5\textwidth}

%%     \end{columns}

%% \end{frame}

@@

\section{Privacy in Fiction}

%% \begin{frame}

%% \begin{columns}[c] % the "c" option specifies center vertical alignment
%%     \column{.5\textwidth} % column designated by a command

%%     \begin{block}{}
%%       Privacy in Fiction.
%%     \end{block}

%%     \column{.5\textwidth}

%%     \end{columns}

%% \end{frame}

@@

\section{Privacy in Film}

%% \begin{frame}

%% \begin{columns}[c] % the "c" option specifies center vertical alignment
%%     \column{.5\textwidth} % column designated by a command

%%     \begin{block}{}
%%       Privacy in Film.
%%     \end{block}

%%     \column{.5\textwidth}

%%     \end{columns}

%% \end{frame}

@@

\section{Discussion Ideas}
